---
title: "Unit 1 - 3 Review Starter"
author: "TALC group 1"   
date: "10/4/2021"
output: html_document 
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
sand_minerals <- read_csv("data/sand-minerals.csv")
location_descriptions <- read_csv("data/location-descriptions.csv")
density <- read_csv("data/density.csv")
solubility_hardness <- read_csv("data/solubility-hardness.csv")
```

## Exercises

### Exercise 1

```{r inspect-sand-minerals} 

glimpse(sand_minerals)
names(sand_minerals)

```

There are `r nrow(sand_minerals)` rows and `r ncol(sand_minerals)` columns

### Exercise 2

```{r inspect-other-dataframes}

glimpse(location_descriptions) 
glimpse(density) 
glimpse(solubility_hardness) 
names(location_descriptions) 
names(density) 
names(solubility_hardness) 

```

In location_descriptions there are `r nrow(location_descriptions)` rows and `r ncol(location_descriptions)`, in density there are `r nrow(density)` rows and `r ncol(density)`, and in solubility_hardness there are `r nrow(solubility_hardness)` rows and `r ncol(solubility_hardness)`.

For location_descriptions, the rows are the location number and the location description. For density, the rows are the mineral names and their density. For solubility_hardness, the rows are the mineral names, the solubility, and the hardness.

### Exercise 3

Remove this text, and add your answer for Exercise 3 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.
